### 2024-05-26 getting-started.qmd
20240526 - clean up
20240526 - long to wide; wide to long

dim(distinct(nfl_actualStats_offense_weekly, player_id, season, week, .keep_all = TRUE))

str(nfl_actualStats_offense_weekly[,c("player_id", "season", "week")])
```

@@

>>>>

dim(distinct(nfl_actualStats_offense_weekly, player_id, season, week, .keep_all = TRUE))
```

@@

## Transform Data from Long to Wide {#sec-longToWide}

Original data:

```{r}
dataLong <- nfl_actualStats_offense_weekly %>% 
  select(player_id, player_display_name, season, week, fantasy_points)

dataLong
```

Data widened by two variable (`season` and `week`), using `tidyverse`:

```{r}
dataLong %>% 
  pivot_wider(
    names_from = week,
    names_glue = "{.value}_week{week}",
    values_from = fantasy_points)

dataLong %>% 
  pivot_wider(
    names_from = c(season, week),
    names_glue = "{.value}_{season}_week{week}",
    values_from = fantasy_points)
```

## Transform Data from Wide to Long {#sec-wideToLong}

Original data:

```{r}
dataWide <- nfl_actualStats_offense_weekly %>% 
  select(player_id, player_display_name, season, week, recent_team, opponent_team)

dataWide
```

Data in long form, transformed from wide form using `tidyverse`:

```{r}
dataWide %>% 
  pivot_longer(
    cols = c(recent_team, opponent_team),
    names_to = "role",
    values_to = "team")
```
